Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-03 manuscript-md/index.Rmd
Add Mike's suggestions to summary

* We investigated whether global leaf economic relationships across plant functional types (PFTs) area also present within-PFTs, and the extent to which this hierarchical structure can be used to constrain trait estimates.

>>>>

* We investigated whether global leaf economic relationships across plant functional types (PFTs) are also present within-PFTs, and the extent to which this hierarchical structure can be used to constrain trait estimates.
